Open-source landscape for 3D CSEM modelling

### 2020-05-18 manuscript/Manuscript.tex
Assimilated changes

\imycom[RR]{We need to take care to not mix British English with AE, I'm very used to AE, but Dieter started with (at least what I can identify) mainly BE, so I tried to follow (mainly s instead of z and ou instead of o in some words). I hope there are not too many inconsistencies, as probably Lindsey has to fix all these mistakes in the end:-)}

>>>>

\imycom[RR]{We need to take care to not mix British English with AE, I'm very
  used to AE, but Dieter started with (at least what I can identify) mainly BE,
  so I tried to follow (mainly s instead of z and ou instead of o in some
  words). I hope there are not too many inconsistencies, as probably Lindsey
  has to fix all these mistakes in the end:-)}
\imycom[DW]{Be aware of Canadian English and Australian English :-D -- You are
  of course right. I am usually mostly BE, having done my PhD in Scotland.
  However, I don't think it matters at the moment, because it will depend to
  what journal we submit. With an appropriate spellchecker that should be a
  quick thing then.}
